### 2016-07-22 Theorem1_FP.tex
Modified proof Theorem1

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{3}(A)$}\\
$\calY \gets \emptyset $\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
$z_1,\cdots, z_t \getsr \calY $\\
if $\exists i\in[1,t] \,\mbox{s.t.} \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$\calY \gets \calY \cup x$\\
Ret $\Qry^{\HashOracle}(M,x)$\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr \Func(\univ,[m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\

if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}
\noindent
From \Cref{eq:m1,eq:m2,eq:m3,eq:m4}, \acnote{compacted} \tsnote{this can be compacted}
\begin{align}
\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
\nonumber& &\\
\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
 \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2a}
\end{align}

\noindent
Adding \Cref{eq:1,eq:2a}, we have
\begin{equation}
\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2}
\end{equation}

\noindent
In $\game{3}(A)$, $t$ elements are sampled from the $q$ queries with probability  $1/\dbinom{q}{t}$ and tested for false positives. So, 
\begin{equation}
\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{t}}\times\Prob{\game{3}(A)=1}\label{eq:3}
\end{equation}

\noindent
The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries and $A'$ is one such adversary simulating $\game{3}(A)$. \acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.  It suffices to say this.} From \Cref{fig:AGame3} and $\game{3}(A)$, it is evident that
\begin{align}
\nonumber \Prob{\game{3}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
& \leq q\times(1-e^{-kn/m})^k \label{eq:4}
\end{align}

%\caption{Adversary $A'$ simulating $\game{3}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.4}{
$\adversaryv{A'^{\HashOracle}}$\\
$\calY \gets \emptyset $ \\
$\ell \getsr [q]$\\
$c = 0$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge c = c + 1$\\
\nudge if $c == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
$\nudge$ $\nudge \calY \gets \calY \cup x$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ'$\\
\nudge $z \gets \calY$\\
\nudge if $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
\caption{\Cref{thm1}:Adversary $A'$ simulating $\game{3}(A)$} \label{fig:AGame3}
\end{figure}

\noindent
From \Cref{eq:0,eq:2,eq:3,eq:4} \\
\begin{align}
\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
\end{align}
\end{proof}

>>>>

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{3}(A)$}\\
$\calY \gets \emptyset $\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calY| < t$ then \\ 
\nudge Ret 0\\
for $i=1$ to $t$ \\
\nudge $z_i \getsr \calY $\\
\nudge $\calY \gets \calY \setminus \{z_i\}$\\
\nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
\nudge \nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$\calY \gets \calY \cup \{x\}$\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$\calS \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr \Func(\univ,[m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

%
\noindent
From \Cref{eq:m1,eq:m2,eq:m3,eq:m4}, %\acnote{compacted} \tsnote{this can be compacted}
\begin{align}
\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
\nonumber& &\\
\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
 \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2a}
\end{align}

\noindent
Adding \Cref{eq:1,eq:2a}, we have
\begin{equation}
\AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2}
\end{equation}

\noindent
In $\game{3}(A)$, $t$ elements are sampled from the $q$ adaptive queries and tested for false positives. This is equivalent to $\game{2}(A)$, as the hash functions of the $\HashOracle$ oracle are random and $A$ wins this  game only if it outputs atleast $t$ FP's.\acnote{I was facing problems in connecting game2(adaptive) and game3(non-adaptive). I felt that the probability of  winning both games should be equal as the hash functions in the hash oracle are random(not independent) and adversary in game 2 has no means to output t elements which have higher chance of winning than those in game 3.}
\begin{equation}
\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
\end{equation}

\noindent
The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and $D$ is one such adversary simulating $\game{3}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $t=1$. $D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.  %\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.  It suffices to say this.}
From \Cref{fig:AGame3}, it is evident that
\begin{align}
\Prob{\game{3}(A)=1} &= \Prob{D \, \mbox{outputs $t$ FP} \,}\label{eq:4a}\\
\nonumber \Prob{D \, \mbox{outputs t FP} \,} &= \dbinom{q}{t}\times \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^t\\
& \leq \dbinom{q}{t}\times \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^t \label{eq:4b}
\end{align}
From \Cref{eq:4a,eq:4b}
\begin{equation}
\Prob{\game{3}(A)=1} \leq \dbinom{q}{t}\times [(1-e^{-kn/m})^k +O(1/n)]^t \label{eq:4}
\end{equation}
%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.8}{
\hpagessl{.5}{.4}
{
$\adversaryv{D^{\HashOracle}}$\\
$\calY, \calZ \gets \emptyset $ \\
$\rho \getsr Func(U,[m])$\\
$\calS \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge \calY \gets \calY \cup {x}$\\
$\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ'$\\
\nudge if $|\calZ'|<t \, \mbox{or} \, |\calY| < t$\\
\nudge \nudge Ret $\emptyset$\\
\nudge for $i=1$ to $t$ \\
\nudge \nudge $z_i \getsr \calY $\\
\nudge \nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
\nudge \nudge Ret $\emptyset$\\
\nudge \nudge $\calZ \gets \calZ \cup z_i$\\
\nudge \nudge $\calY \gets \calY \setminus {z_i}$\\
\nudge Ret $\calZ $\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
$\adversaryv{D'^{\HashOracle}}$\\
$\calY \gets \emptyset $ \\
$\ell \getsr [q]$\\
$c = 0$\\
$\rho \getsr Func(U,[m])$\\
$\calS \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge c = c + 1$\\
\nudge if $c == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ'$\\
\nudge $z \gets \calY$\\
\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
\nudge \nudge Ret $z$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
\end{figure}

\noindent
From \Cref{eq:0,eq:2,eq:3,eq:4} \\
\begin{align}
\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} +
\AdvPRF{F}{B_2}  +{\dbinom{q}{t}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^t
\end{align}
\end{proof}
